\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.6in]{geometry}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

\hypersetup{colorlinks=true, linkcolor=blue}

\definecolor{p}{RGB}{225,29,72}
\definecolor{s}{RGB}{13,148,136}
\definecolor{a}{RGB}{245,158,11}
\definecolor{d}{RGB}{15,23,42}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textbf{LifeLink} --- Viva Cheat Sheet}
\fancyfoot[C]{\thepage}

\titleformat{\section}{\large\bfseries\color{d}}{}{0em}{}[\color{p}\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{d}}{}{0em}{}

\setlist[itemize]{leftmargin=*, nosep, topsep=0pt}
\setlist[enumerate]{leftmargin=*, nosep, topsep=0pt}
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}

\begin{document}

% ══════════════════════════════════════════════════════════════════════════
\section{What is LifeLink?}
% ══════════════════════════════════════════════════════════════════════════

A \textbf{web-based blood and organ donor matching platform} that connects donors, hospitals, and patients during medical emergencies. Users search by blood group/location, get matched with available donors, and communicate via chat or masked calling.

\textbf{One-liner:} ``Search engine for saving lives --- find blood/organ donors near you in seconds.''

% ══════════════════════════════════════════════════════════════════════════
\section{Tech Stack}
% ══════════════════════════════════════════════════════════════════════════

\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Frontend} & React 19, Vite, React Router v7, Axios, Custom CSS (Glassmorphism) \\
\textbf{Backend} & Node.js, Express.js, Joi (validation) \\
\textbf{Database} & MongoDB, Mongoose \\
\textbf{Auth} & JWT (30-day), bcrypt (10 rounds), Google OAuth \\
\textbf{Real-Time} & Server-Sent Events (SSE) \\
\textbf{Push} & Firebase Cloud Messaging (FCM) \\
\textbf{Location} & Browser Geolocation API + Nominatim (OpenStreetMap) \\
\textbf{Security} & Helmet, express-rate-limit (500 req/15min) \\
\textbf{Deploy} & Docker Compose, Vercel \\
\end{tabularx}

% ══════════════════════════════════════════════════════════════════════════
\section{MERN Stack Explained}
% ══════════════════════════════════════════════════════════════════════════

\textbf{M}ongoDB (database) $\rightarrow$ \textbf{E}xpress.js (backend framework) $\rightarrow$ \textbf{R}eact.js (frontend) $\rightarrow$ \textbf{N}ode.js (runtime)

\begin{itemize}
    \item \textbf{React} --- Component-based UI library. Used for building reusable UI components (DonorCard, Modal, Chat).
    \item \textbf{Express} --- Minimal Node.js web framework. Handles routes, middleware, API logic.
    \item \textbf{MongoDB} --- NoSQL document database. Flexible schema for nested user profiles.
    \item \textbf{Node.js} --- JavaScript runtime. Runs the backend server.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════
\section{Database --- 7 Collections}
% ══════════════════════════════════════════════════════════════════════════

\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{User} & email, phone, password, role (donor/hospital/admin), profile (nested), blockedIds, fcmToken \\
\textbf{Donor} & user ref, bloodGroup, organType, city, location (2dsphere), available \\
\textbf{Hospital} & user ref, hospitalName, email, phone, city, location, verified \\
\textbf{Request} & requestType, bloodGroup, organType, hospital ref, matchedDonor ref, status, isEmergency \\
\textbf{Message} & sender ref, receiver ref, text, read \\
\textbf{Notification} & user ref, title, message, type, read, redirect \\
\textbf{CallLog} & user ref, donorId, bloodGroup, age, gender, city, direction \\
\end{tabularx}

\textbf{Relationships:} User 1:1 Donor, User 1:1 Hospital, Hospital 1:N Request, Donor 1:N Request, User 1:N Message, User 1:N Notification

% ══════════════════════════════════════════════════════════════════════════
\section{Key Algorithms}
% ══════════════════════════════════════════════════════════════════════════

\subsection{Donor Auto-Matching}
\begin{enumerate}
    \item Hospital creates request with bloodGroup/organType + city
    \item System queries Donor collection: \texttt{donorType + city + available + bloodGroup}
    \item If match found $\rightarrow$ auto-assign, mark unavailable, notify (SSE + email + push)
    \item If no match + emergency $\rightarrow$ alert ALL matching donors in that city
\end{enumerate}

\subsection{Haversine Distance Formula}
\[
d = 2R \cdot \arcsin\left(\sqrt{\sin^2\left(\frac{\Delta\phi}{2}\right) + \cos\phi_1 \cdot \cos\phi_2 \cdot \sin^2\left(\frac{\Delta\lambda}{2}\right)}\right)
\]
$R = 6371$ km (Earth radius). Used to sort donors by proximity from user's GPS coordinates.

% ══════════════════════════════════════════════════════════════════════════
\section{Real-Time: SSE vs Socket.IO}
% ══════════════════════════════════════════════════════════════════════════

\begin{itemize}
    \item \textbf{SSE (Server-Sent Events)} --- Used for real-time push from server to client
    \item Client opens \texttt{GET /api/stream?token=xxx} connection
    \item Server pushes events: \texttt{new-notification}, \texttt{new-request}, \texttt{receive-message}, \texttt{online-users}
    \item Chat messages sent via REST API (\texttt{POST /api/chat/:id/send})
    \item Exponential backoff reconnection: 2s, 4s, 8s... max 30s
    \item Heartbeat every 15s keeps connection alive
\end{itemize}

\textbf{Why SSE over Socket.IO?} Simpler setup, automatic reconnection, works through proxies, no WebSocket configuration needed.

% ══════════════════════════════════════════════════════════════════════════
\section{Security Layers}
% ══════════════════════════════════════════════════════════════════════════

\begin{enumerate}
    \item \textbf{Rate Limiting} --- 500 req/15min on /api routes
    \item \textbf{Helmet} --- HTTP security headers (CSP, HSTS, X-Frame-Options)
    \item \textbf{CORS} --- Whitelist of allowed origins
    \item \textbf{JWT} --- Bearer token auth, 30-day expiry
    \item \textbf{Role-based access} --- donor / hospital / admin
    \item \textbf{Joi validation} --- Schema validation on register, login, reset
    \item \textbf{bcrypt} --- Password hashing with 10 salt rounds
\end{enumerate}

\textbf{Privacy:} Donor cards show only age, gender, blood group, weight, city --- NO name/phone/email until user clicks ``Contact Securely.''

% ══════════════════════════════════════════════════════════════════════════
\section{Main Features (Quick List)}
% ══════════════════════════════════════════════════════════════════════════

\begin{multicols}{2}
\begin{itemize}
    \item Email + Google auth
    \item JWT token auth
    \item Profile with medical info
    \item Blood group search
    \item Organ type search
    \item GPS + Pincode location
    \item Distance sorting (Haversine)
    \item Auto donor matching
    \item Emergency alerts
    \item Real-time chat
    \item Typing indicators
    \item Read receipts
    \item Masked calling
    \item Call logs
    \item Notifications (SSE)
    \item Push notifications (FCM)
    \item Block/unblock donors
    \item Account deletion
    \item Dashboard analytics
    \item Docker deployment
\end{itemize}
\end{multicols}

% ══════════════════════════════════════════════════════════════════════════
\section{How Location Search Works}
% ══════════════════════════════════════════════════════════════════════════

\begin{enumerate}
    \item User opens search page
    \item Frontend gets lat/lng from Browser Geolocation API OR pincode lookup
    \item Calls Nominatim reverse geocode to get city name
    \item Sends \texttt{GET /api/search?type=blood\&query=O+\&lat=18.52\&lng=73.85}
    \item Backend filters all complete profiles by donateBlood/donateOrgan + query match
    \item Frontend calculates Haversine distance to each donor
    \item Sorts results nearest-first
    \item Displays DonorCards (age, gender, weight, blood group, city, distance)
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════
\section{Chat System}
% ══════════════════════════════════════════════════════════════════════════

\begin{itemize}
    \item \textbf{Sending:} REST API \texttt{POST /api/chat/:userId/send}
    \item \textbf{Receiving:} SSE event \texttt{receive-message}
    \item \textbf{Typing:} REST API \texttt{POST /api/chat/:userId/typing} $\rightarrow$ SSE \texttt{user-typing}
    \item \textbf{Read receipts:} REST API \texttt{POST /api/chat/:userId/read} $\rightarrow$ SSE \texttt{messages-read}
    \item \textbf{Conversation list:} Aggregation pipeline on Message collection
    \item \textbf{Unread count:} Separate aggregation grouped by sender
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════
\section{Frontend Context Providers}
% ══════════════════════════════════════════════════════════════════════════

\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{AuthProvider} & User state, login/signup/logout, notifications, call logs, blocked donors, FCM \\
\textbf{SocketProvider} & SSE connection, online users, reconnection, chat event dispatch \\
\textbf{LocationProvider} & GPS detection, pincode lookup, current coordinates \\
\end{tabularx}

% ══════════════════════════════════════════════════════════════════════════
\section{Deployment}
% ══════════════════════════════════════════════════════════════════════════

\textbf{Docker Compose:} 3 containers
\begin{itemize}
    \item \textbf{mongodb} --- mongo:latest, port 27017, persistent volume
    \item \textbf{backend} --- Node.js, port 5000, depends on mongodb
    \item \textbf{frontend} --- React + Vite, port 5173, depends on backend
\end{itemize}

\textbf{Production:} Frontend on Vercel, Backend on Render, MongoDB Atlas

% ══════════════════════════════════════════════════════════════════════════
\section{Limitations (Be Honest)}
% ══════════════════════════════════════════════════════════════════════════

\begin{itemize}
    \item OTP is hardcoded (123456) --- no real SMS
    \item Medical verification checks filename only
    \item Masked calling is a 2.5s timer simulation
    \item Certificates stored as base64 (not scalable)
    \item Pincode table has only 10 cities
    \item No real SMTP email configured
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════
\section{Future Enhancements}
% ══════════════════════════════════════════════════════════════════════════

\begin{multicols}{2}
\begin{itemize}
    \item Twilio/MSG91 for real OTP
    \item WebRTC for actual calling
    \item AI donor recommendation
    \item React Native mobile app
    \item Government health integration
    \item Multi-language support
    \item OCR certificate verification
    \item Video calling
    \item Global expansion
    \item Blockchain verification
\end{itemize}
\end{multicols}

% ══════════════════════════════════════════════════════════════════════════
\section{Quick Q\&A for Viva}
% ══════════════════════════════════════════════════════════════════════════

\textbf{Q: Why MongoDB over MySQL?}\\
A: Flexible schema for nested user profiles. No complex joins needed. Geospatial index (2dsphere) for location queries.

\textbf{Q: Why SSE over WebSocket?}\\
A: Simpler, automatic reconnection, works through HTTP proxies, no special server config. Our use case is server-to-client push (notifications), not bidirectional.

\textbf{Q: How does the Haversine formula work?}\\
A: Calculates great-circle distance between two lat/lng points on Earth. Uses Earth radius (6371km) and trigonometry. More accurate than Euclidean distance for geographic coordinates.

\textbf{Q: What is glassmorphism?}\\
A: UI design trend with translucent ``glass'' backgrounds, backdrop blur, subtle borders. Used in our dashboard cards and modals.

\textbf{Q: How is JWT different from session-based auth?}\\
A: JWT is stateless --- server doesn't store session. Token contains user ID, signed with secret. Every request carries the token. No server-side session store needed.

\textbf{Q: What is role-based access control?}\\
A: Users have roles (donor, hospital, admin). Certain routes check the role before allowing access. E.g., only hospitals can create requests.

\textbf{Q: What is 2dsphere index?}\\
A: MongoDB index for geospatial queries. Enables ``find documents within X radius of a point'' queries. Used in Donor and Hospital collections.

\textbf{Q: How does Docker Compose help?}\\
A: Defines 3 services (mongo, backend, frontend) in one file. Single command starts everything. Volumes for data persistence. Dependencies managed automatically.

\end{document}
